% -*- coding:utf-8 -*-
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\newenvironment{note}{\paragraph{NOTE:}}{}
\newenvironment{field}{\paragraph{field:}}{}
\begin{document}
\begin{note}
   \begin{field}
       Give the value of the gravitational parameter of Earth (\(\mu_earth\)) with a significance of 3 digits, along with its units (using frac if necessary).
   \end{field}
   \begin{field}
		\[
			3.986\cdot10^5\frac{km^3}{s^2}
		\]
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       Give the gravitational parameter of the moon in 1 significant digit, along with its units (using frac if necessary).
   \end{field}
   \begin{field}
		\[
			4.9\cdot10^{3}\frac{kg^3}{s^2}
		\]
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       Give the value of the gravitational parameter of the Sun (\(\mu_{Sun}\)) with a significance of 5 digits, along with its units (using frac if necessary).
   \end{field}
   \begin{field}
		\[
			1.32712\cdot10^{11}\frac{km^3}{s^2}
		\]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       Give the mass of Jupiter in 1 digit in kg.
   \end{field}
   \begin{field}
		\[
			2\cdot10^{27}kg
		\]
   \end{field}
\end{note}
%%%

\begin{note}
   \begin{field}
       Give the gravitational constant in 3 significant digits, along with its units (using frac if necessary).
   \end{field}
   \begin{field}
		\[
			6.674\frac{m^3}{kg s^2}
		\]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       Give the value of 1AU with a significance of 3 digits in meters.
   \end{field}
   \begin{field}
		\[
			1.496\cdot10^6m
		\]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       Give the radius of Earth in km.
   \end{field}
   \begin{field}
		\[
			6378km
		\]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       Give the diameter of the Sun, as seen from Earth in degrees.
   \end{field}
   \begin{field}
		\[
			0.54 degrees
		\]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       Give the speed of light in 3 significant digits, along with its units (using frac if necessary).
   \end{field}
   \begin{field}
		\[
			2.998\frac{m}{s}
		\]
   \end{field}
\end{note}
\end{document}