% -*- coding:utf-8 -*-
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\newenvironment{note}{\paragraph{NOTE:}}{}
\newenvironment{field}{\paragraph{field:}}{}
\begin{document}
\section{Solar System Dynamics}
\begin{note}
   \begin{field}
       In: \(R_{min}=\sqrt{\frac{2S}{\pi G \rho^2}}\), what is \(S\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		The internal strength of the material,
		\[
			\frac{N}{m^2}
		\]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       In: \(T = \frac{1-A_B}{4\epsilon\sigma}\frac{F}{d^2}\), what is \(A_B\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		Bond Albedo,[-]	
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       In: \(T = \frac{1-A_B}{4\epsilon\sigma}\frac{F}{d^2}\), what is \(\epsilon\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		emessivity of the body,[-]
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       In: \(T = \frac{1-A_B}{4\epsilon\sigma}\frac{F}{d^2}\), what is \(F\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		Solar constant, equivalent of radiation,[-]
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       In: \(T = \frac{1-A_B}{4\epsilon\sigma}\frac{F}{d^2}\), what is \(d\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		Distance between star and body,[AU]
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       In: \(N_p(t)=e^{-\frac{t-t_0}{\tau_m}}N_p(t_0)\),  what is \(N_p\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		The fraction of isotopes.
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       In: \(N_p(t)=e^{-\frac{t-t_0}{\tau_m}}N_p(t_0)\),  what is \(\tau_m\)? Commaseparate the answer with its units. (using frac if necessary).
   \end{field}
   \begin{field}
		The mean life time \(t_{1/2}=ln(2)\tau_m\) and \(\lambda=\frac{1}{\tau_m}\)
   \end{field}
\end{note}
\end{document}