% -*- coding:utf-8 -*-
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\newenvironment{note}{\paragraph{NOTE:}}{}
\newenvironment{field}{\paragraph{field:}}{}
\begin{document}
\begin{note}
   \begin{field}
       Give 2 reasons why it  is difficult to detect exoplanets using imaging. Start numbering as: 0. Reason.
   \end{field}
   \begin{field}
		0. Exoplanets are faint with respect to the star they orbit.
		1. Exoplanets orbit their stars relatively close.
   \end{field}
   \begin{field}
		Because they orbit their star so close, it is difficult to distinguish them from the star, and they might be obfuscated by the star for a large fraction of their orbit.
   \end{field}
\end{note}
%%%
%%%
\begin{note}
   \begin{field}
       Give the order of the solar planets from inside to outside, commaseparated
   \end{field}
   \begin{field}
		Mercury, Venus, Earth Mars, Jupiter, Saturn, Uranus, Neptune
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What are the terrestrial planets?
   \end{field}
   \begin{field}
		Mercury, Venus, Earth Mars
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       Give 4 similarities between the radial structure of the terrestrial planets. Start numbering as: 0. Reason.
   \end{field}
   \begin{field}
		0. Iron/nickel core
		1. Mantle with sillicates
		2. Outer lithosphere
		3. Similar order of magnitude of size
   \end{field}
   \begin{field}
		Because they orbit their star so close, it is difficult to distinguish them from the star, and they might be obfuscated by the star for a large fraction of their orbit.
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       Give 3 reasons why an albedo can change. Start numbering as: 0. Reason.
   \end{field}
   \begin{field}
		0. The surface of a body might change while it rotates.
		1. Weather may change the reflectivity of the body.
		2. The composition of the atmosphere of the body may change locally,  yielding a different reflectivity.
   \end{field}
   \begin{field}
   \end{field}
\end{note}

\end{document}