% -*- coding:utf-8 -*-
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\newenvironment{note}{\paragraph{NOTE:}}{}
\newenvironment{field}{\paragraph{field:}}{}
\begin{document}

%%%
\begin{note}
   \begin{field}
       Name the orbital types that occasionaly fly by Earth. Use commaseparated alphabetical ordering.
   \end{field}
   \begin{field}
		asteroids, comets, meteoroids, meteors
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is the difference between an asteroid and a meteoroid?
   \end{field}
   \begin{field}
		A meteoroid is a piece of broken off asteroid.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is the difference between an meteoroid and a meteor?
   \end{field}
   \begin{field}
		A meteor is when a meteoroid or comet hits Earth atmosphere.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is the difference between an asteroid and a comet?
   \end{field}
   \begin{field}
		Comets are made of dust and ice, asteroids are made of rock.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is the difference between an meteoroid and a meteorite?
   \end{field}
   \begin{field}
		A meteorite is when a meteoroid hits Earth surface.
   \end{field}
   \begin{field}
   \end{field}
\end{note}

%%%
\begin{note}
   \begin{field}
       Give 5 types of meteorites. Use commaseparated alphabetical ordering.
   \end{field}
   \begin{field}
		achondritics, chondrites, chondrules, iron meteorites, stony-iron meteorites, moon meteoroids, pallasites
   \end{field}
   \begin{field}
   \end{field}
\end{note}


%%%
\begin{note}
   \begin{field}
       What is a chondrite?
   \end{field}
   \begin{field}
		A non-molten, non-differentiated stony meteorite from the early solar system.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is a chondrule?
   \end{field}
   \begin{field}
		A grain which has been molten and accreeted on the chrondrite.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is are achondritics?
   \end{field}
   \begin{field}
		Meteor with origin of differentiated bodies, near the surface of asteroids or planets.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%
\begin{note}
   \begin{field}
       What is a pallasite?
   \end{field}
   \begin{field}
		Solidified magma, from core or molten mantle of asteroid.
   \end{field}
   \begin{field}
   \end{field}
\end{note}
%%%

\end{document}